% Acknowledgments
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

\begin{flushright}{
	\slshape
	Ahora que el tiempo ha pasado,\\ 
	doy gracias por haber llegado hasta aqu\'i.

	--- Enrique Bunbury, \emph{Ahora}.
}
\end{flushright}



\bigskip

\begingroup
	\let\clearpage\relax
	\let\cleardoublepage\relax
	\let\cleardoublepage\relax
	\chapter*{Acknowledgments}
		This thesis would not exist without the help, patience, and kindness of many
		people during the lengthy PhD process. I extend my deepest gratitude to
		all of them.

		Primero, y más importante, debo agradecer a mi familia. A mis padres (Reyna
		y Juan Jos\'e Tejada), y hermanita (Katherine Tejada). Gracias por todo el
		apoyo, amor, y paciencia durante este largo y arduo proceso. No tengo
		palabras para agradecerles por todo lo que hacen. Al resto de mi querida
		familia Tejada--Modesto en la Rep\'ublica Dominicana, gracias por siempre
		estar atentos a mi bienestar. Finalmente a mi segunda familia, los Alonzo,
		gracias por todo el apoyo, consejos, risas, y comidas.
		
		This thesis would not have been completed without the advice, guidance, and
		patience from my supervisor Dan Ashbrook. Thank you for taking a chance with
		an grad student who clearly had no idea what he was doing.

		Continuing, I owe a huge debt of gratitude to all my coauthors: Jess
		McIntosh, Sebastian Boring, Raf Ramakers, Mengyu Zhong, Hyunyoung Kim, Osamu
		Fujimoto, Zhiyuan Li, Aluna Everitt, and Azier Marzo. Thank you for your
		hard work, and thoughtful comments. Naturally, this thesis would not exist
		without them.

		Last, but certainly not least, I am indebted to my wonderful colleagues at
		the Human-Centered Computing Section from the Department of Computer Science
		in the University of Copenhagen. Kasper Hornb\ae{}k, Pernille Bjørn, Irina
		Shklovski, Joanna Bergstr\"om, Henning Pohl, Hyunyoung Kim, Jess McIntosh,
		Jonas Schjerlund, Andreea Muresan, Tor-Salve Dalsgaard, Klemen Lilija, 
		Xiaoyi Wang, and Aske Mottelson. Thank you for your the thoughtful
		scientific (and also for the non-scientific) discussions, laughs, beers, and
		for making the conference crunching time a lot more bearable.

		\vfill

		\noindent
		Carlos E. Tejada\\
		Copenhagen, 2021

\endgroup
